Deep Blockchains

### 2018-07-08 paper/main.tex
add hyperlinks, smt license and copyright notice
Bandwidth section update

\usepackage{url}
\usepackage{amsfonts}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage[nottoc]{tocbibind}
\geometry{left=.75in,top=.75in,right=.75in,bottom=1.0in}

@@

\begin{enumerate}
\item {\em Bandwidth} is paid for through (1) signed  \texttt{retrieveChunk}$(k, \tau, \signature)$ calls to retrieve data and obtain recent balances, where each call uses up a tiny amount of bandwidth backed for with a token $\tau$ originated by the \texttt{createBlockchain} call; (2) signed a new \texttt{updateBalance} call to agree to recent balances;

>>>>

\usepackage{url}
\usepackage{amsfonts}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
\usepackage[nottoc]{tocbibind}
\geometry{left=.75in,top=.75in,right=.75in,bottom=1.0in}

@@

\begin{enumerate}
\item {\em Bandwidth} is paid for through (1) users signing  \texttt{retrieveChunk}$(k, \tau, \signature)$ calls to retrieve data and obtaining recent balances, where each call uses up a tiny amount of bandwidth backed for with a token $\tau$ originated by the \texttt{createBlockchain} call; (2) users signing a new \texttt{updateBalance}$(\tau, \balance, \signature)$ request originated by operator and agreeing to making a payment for incurred bandwidth usage and the latest token owner balance. An \texttt{updateBalance} response by users is mapped into layer2 transaction, where incurred bandwidth cost is deducted from token's owner balance $\balance(\tau)$ and added to operator's allowance $\allowance(\tau)$.
